Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-23 ICML2019/main.tex
working on section 3 and 4.

\noindent \textbf{Hellinger distance.}
\emph{Hellinger} distance $\hellinger(\cdot,\cdot)$ is a statistical
divergence measuring the distance between two probability
distributions. Given two probability distributions $\textup{P}$ and $\textup{Q}$,
the Hellinger distance between them is defined as:
\[
\hellinger(P,Q) =\sqrt{\frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda}
\]
When $\textup{P}=\betad(\alpha_1, \beta_1)$ and $\textup{Q}=\betad(\alpha_2, \beta_2)$, we can unfold the above and derive: 
\[
 \hellinger(P,Q) =  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]

@@

We will use the \emph{Hellinger} distance $\hellinger(\cdot,\cdot)$.
Given two probability distributions $\textup{P}$ and $\textup{Q}$,
the square of the Hellinger distance between them is defined as:
\[
\hellinger(P,Q)^2 =\frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda
\]
When $\textup{P}=\dirichlet{\valpha_1}$ and $\textup{Q}=\dirichlet{\valpha_2}$, we can unfold the above and derive: 
 \[
   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}}
 \]
Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
  \item It simplifies calculations in the case of the probabilistic models considered here.

  \item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage an adversary can have in distingishing two distributions.

  \item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. Indeed, as shown in Figure \ref{fig_sensitivity}, there can be a gap
    between the global sensitivity and the local sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
\caption{Local sensitivity of $\hellinger$. Data size is 100. $\alpha$ is the number of 1s.}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

>>>>

\noindent \textbf{Hellinger distance.}
The \emph{Hellinger} distance $\hellinger(\cdot,\cdot)$ is a statistical
divergence measuring the distance between two probability
distributions. Given two probability distributions $\textup{P}$ and $\textup{Q}$,
the Hellinger distance between them is defined as:
\[
\hellinger(P,Q) =\sqrt{\frac{1}{2} \int \bigg(\frac{dP}{d \lambda} - \frac{dQ}{d \lambda}\bigg)^2 d \lambda}
\]
When we consider the Hellinger distance between Dirichlet
distributions we can simplify this definition to close form. If $\textup{P}=\dirichlet{\valpha_1}$ and
$\textup{Q}=\dirichlet{\valpha_2}$ we have: 
 \[
   \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}}
 \]

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.32\textwidth]{sensitivity_2d.eps}
\caption{Local sensitivity of $\hellinger$. Data size is 100. $\alpha$ is the number of 1s.}
\label{fig_sensitivity}
\end{figure}
